Staged Abstract Interpreters

### 2019-09-09 paper/20_prelim.tex
typo

\paragraph{Concrete Components}
The two types we need to concretize are addresses @Addr@ and values @Value@. The
types @Env@ and @Store@ are derived automatically. To ensure the freshness of
address allocations, we use type @Int@ and always return a number greater
than the size of the current store.
A value can be either a tagged number \texttt{IntV}, or a closure
\texttt{CloV} that contains a lambda term and an environment. The final
result of the interpreter is a pair of values and stores.
To distinguish from the monadic values of type @Ans@ produced by the
interpreter, later we use term \textit{grounded values} to denote such final values.
The two elements in the type @Result@ are annotated by the binding-time @R@,
because they cane be next-stage objects.  We also define a standard fixed-point
combinator to close the open-recursive function @ev@.
\begin{lstlisting}
  trait ConcreteComponents extends Semantics {
    type Addr = Int;  sealed trait Value
    case class IntV(i: Int) extends Value
    case class CloV(λ: Lam, e: Env) extends Value
    type Result = (R[Value], R[Store])
    def fix(ev: (Expr => Ans) => (Expr => Ans)): Expr => Ans = e => ev(fix(ev))(e)
  }
\end{lstlisting}

>>>>

\paragraph{Concrete Components}
The two types we need to concretize are addresses @Addr@ and values @Value@. The
types @Env@ and @Store@ are derived automatically. To ensure the freshness of
address allocations, we use type @Int@ and always return a number that is greater
than the size of the current store.
A value can be either a tagged number \texttt{IntV}, or a closure
\texttt{CloV} that contains a lambda term and an environment. The final
result of the interpreter is a pair of values and stores.
To distinguish from the monadic values of type @Ans@ produced by the
interpreter, later we use term \textit{grounded values} to denote such final values.
The two elements in the type @Result@ are annotated by the binding-time @R@,
because they can be next-stage objects.  We also define a standard fixed-point
combinator to close the open-recursive function @ev@.
\begin{lstlisting}
  trait ConcreteComponents extends Semantics {
    type Addr = Int;  sealed trait Value
    case class IntV(i: Int) extends Value
    case class CloV(λ: Lam, e: Env) extends Value
    type Result = (R[Value], R[Store])
    def fix(ev: (Expr => Ans) => (Expr => Ans)): Expr => Ans = e => ev(fix(ev))(e)
  }
\end{lstlisting}
